\ttitle

### 2015-06-23 Chapters/CPET_Survival.tex
Add CPET vs 6, 12, 24 month survivor tables
- Compare CPET in survivors vs non-survivors at 6, 12, 24 months
- Include these tables in chapter
- TODO - describe these tables in the results section
- TODO - Kaplan-Meir plots

Fifty patients (31 male) with pancreatic ductal adenocarcinoma underwent pancreaticoduodenectomy (n=48) or sub-total pancreatectomy (n=2) and had cardiopulmonary exercise test as part of their preoperative assessment. The median age of the patients was xx (range ). Three patients died within 30 days of the operation as a result of postoperative complications and were excluded from the survival analysis.

@@

%Create a table looking at means of cardiopulmonary exercise test parameters in survivors vs. non-survivors at 6 months, 1 year and 2 years. This should give three tables. as below.

\input{Tables/cpet_survival_6months}

>>>>

Fifty patients (31 male) with pancreatic ductal adenocarcinoma underwent pancreaticoduodenectomy (n=48) or sub-total pancreatectomy (n=2) and had cardiopulmonary exercise test as part of their preoperative assessment. The median age of the patients was 66 years (IQR 57 - 70 years ). Three patients died within 30 days of the operation as a result of postoperative complications and were excluded from the survival analysis.

@@

%Create a table looking at means of cardiopulmonary exercise test parameters in survivors vs. non-survivors at 6 months, 1 year and 2 years. This should give three tables as below.

Cardiopulmonary exercise testing parameters in survivors and non-survivors at 6 months, 12 months and 24 months are shown in tables \ref{table:cpet_survival_6months}, \ref{table:cpet_survival_12months}, \ref{table:cpet_survival_24months}.

\input{Tables/cpet_survival_6months}
\input{Tables/cpet_survival_12months}
\input{Tables/cpet_survival_24months}
